### 2014-03-14 docs/paper.tex
Mention scanning resistance earlier.

Broadly speaking, there are two main challenges to proxy-based circumvention:
blocking by content and blocking by endpoint.
Blocking by content means that the censor inspect packet or flow payloads,
looking, for example, for forbidden protocols or keywords.
Content-based blocking is countered by obfuscation:
making circumvention traffic difficult to distinguish
from traffic the censor wishes to allow.
Blocking by endpoint means that the censor forbids all communication with certain
network addresses, whatever the content of the communication.
The challenge of endpoint blocking is met by making it difficult for the censor to learn proxy addresses;
by having sufficiently many proxies;
or by colocating proxies with high-value services, to block which would incur collateral damage.
Effective proxy-based circumvention requires that both these challenges be addressed.

>>>>

Broadly speaking, there are two main challenges to proxy-based circumvention:
blocking by content and blocking by endpoint.
Blocking by content means that the censor inspect packet or flow payloads,
looking, for example, for forbidden protocols or keywords.
Content-based blocking is countered by obfuscation:
making circumvention traffic difficult to distinguish
from traffic the censor wishes to allow.
Blocking by endpoint means that the censor forbids all communication with certain
network addresses, whatever the content of the communication.
The challenge of endpoint blocking is met by making it difficult for the censor to learn proxy addresses;
by making it difficult to scan for proxies;
by having sufficiently many proxies;
or by colocating proxies with high-value services, to block which would incur collateral damage.
Effective proxy-based circumvention requires that both these challenges be addressed.
